A Global Picture of Food Insecurity and Hunger

### 2020-09-07 docs/modeling_fies.tex
Note about improvements in some African countries

Globally, in the year 2020, we estimate that 2.33 billion people experience at least moderate food insecurity, and 829 million people experience severe food insecurity (See Fig. \ref{fig:timeseries}).  While the total number of people in moderate and severe food security held roughly constant for the 2010s and even increased in latter part of that decade, we predict that it will decline throughout the 2020s.  However, this overall decline will not be uniform across the world.  Our model expects that, in sub-Saharan Africa, moderate food insecurity will increase throughout the 2020s and severe food insecurity will plateau.  Food Security will fall in most other world regions, particularly South Asia and East Asia \& the Pacific.

>>>>

Globally, in the year 2020, we estimate that 2.33 billion people experience at least moderate food insecurity, and 829 million people experience severe food insecurity (See Fig. \ref{fig:timeseries}).  While the total number of people in moderate and severe food security held roughly constant for the 2010s and even increased in latter part of that decade, we predict that it will decline throughout the 2020s.  However, this overall decline will not be uniform across the world.  Our model expects that, in sub-Saharan Africa, moderate food insecurity will increase throughout the 2020s and severe food insecurity will plateau, although it will improve in some countires, such as Kenya, Senegal, and Ethiopia.  Food Security will fall in most other world regions, particularly South Asia and East Asia \& the Pacific.
